Computational Luminance Constancy from Naturalistic Images

### 2018-06-28 Draft5/draft5.tex
frustating citation edits

Supervised learning requires large labeled datasets.  Such datasets are not readily available for the study of color constancy. Although there are datasets of calibrated color images, these do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}. There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning. Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors \cite{kovacs17shading}.

@@

% Figure RMSE vs N RFs
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{../FiguresDraft5/Figure13/Figure13.pdf}
\caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set. The relative RMSE converges around 2000 images. To make this plot, the 300 image test set for Condition 3 was used in each case, while the training set size varied between 300 to 2700 images. The number of receptive fields used was varied between 1 and 6. (b) Same data as in panel a, but plotted as a function of number of receptive fields. Performance converges around 3 RFs.}
 \label{fig:RMSEvsRF}
\end{figure}

@@

>>>>

Supervised learning requires large labeled datasets.  Such datasets are not readily available for the study of color constancy. Although there are datasets of calibrated color images, these do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}. There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning. Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors \cite{bell2014intrinsic}.

@@

% Figure RMSE vs N RFs
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{../FiguresDraft5/Figure13/Figure13.pdf}
\caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set. The relative RMSE converges around 2000 images. To make this plot, the 300 image test set for Condition 3 was used in each case, while the training set size varied between 300 to 2700 images. The number of receptive fields used was varied between 1 and 6. (b) Same data as in panel a, but plotted as a function of number of receptive fields. Performance converges around 3 RFs. The error bars in each panel show +/- 1 SEM, with the variation taken across multiple runs with different random initializations for the numerical search used in our implementation of AMA.}
 \label{fig:RMSEvsRF}
\end{figure}

Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
The first two are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted.
In contrast to the Condition 1 RFs, there is also systematic contribution of cone excitations from background object locations, with both positive and negative contributions from background objects. 
The specific geometry of the receptive fields, however, should not be taken to be a strict prediction for receptive fields in the human visual system, as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set. 
Indeed, aspects of spatial structure of the training images can be seen in the RFs. 
Also, the third receptive field for Condition 3 places weight on the S cone excitations.
Although S cone signals do not contribute directly to luminance,  S cone responses are correlated with
L and M cone responses to natural spectra \cite{burton1987color, benson2014unsupervised}.
Information from the S cones can therefore contribute usefully to performance in the task. 
Finally, we note that there is some run-to-run variation in the structure of the optimal receptive fields that depends on the random initialization of the numerical search used in our implementation of AMA. 
(The cost landscape is not convex so local minima are possible.) 
However, such run-to-run RF variation leads only to very small changes in estimation error (see error bars in Figure~\ref{fig:RMSEvsRF}). 
Furthermore, even if the order varies somewhat, the same set of RFs tends to be learned.

@@

\section{Acknowledgments} \label{Acknowledgments}

Supported by startup funds from the University of Pennsylvania (JB), NIH grant R01 EY028571 from the National Eye Institute and the Office of Behavioral and Social Science Research (JB), NIH grant RO1 EY100106 (DHB) from the National Eye Institute, Simons Foundation Collaboration on the Global Brain Grant 324759 (DHB), and the University of Pennsylvania Computational Neuroscience Initiative (VS).  Preliminary versions of this work were presented at the Computational Cognitive Neuroscience Conference (2017) and the Annual Meeting of the Society for Neuroscience (2017).
